### 2023-09-02 sections/2-methods.tex
weak stab at caption

\begin{figure}[ht!]
    \centering
    \includegraphics[width=2.5in]{images/geometry/geometry.pdf}
    \caption{Scaling Behavior of Radii in a Two-Dimensional Uniform-Density Disk}
    \label{fig:methods:scaling_behavior}
\end{figure}

>>>>

\begin{figure}[ht!]
    \centering
    \includegraphics[width=2.5in]{images/geometry/geometry.pdf}
    \caption{Scaling Behavior of Radii in a Two-Dimensional Uniform-Density Disk. $R$ 
    denotes the radius of the root cluster $C$, and $o$ denotes its center. The right 
    triangle formed by $o$, $o'$, and $y+$ in $C'$ shows that $R \leq R'$, where $R'$ is the radius of $C'$.
    Hence, the radius of a child cluster can be larger than its parent. $C''$ 
    illustrates that after we have consumed all $d$ axes, the radius of a child cluster
    is bounded above by $\frac{R}{\sqrt{2}}$.}
    \label{fig:methods:scaling_behavior}
\end{figure}
